---
output: 
  html_document:
    number_sections: false
    df_print: paged
    theme: flatly
    self_contained: true
    css: 'styles.css'
params:
    label: NA
    ome: NA
    size: NA
    num_samples: NA
    num_pools: NA
    samples_per_pool: NA
    protocol: NA
    table_wide: NA
    table_long: NA
    table_long_raw: NA
    table_wide_colnames: NA
    table_long_colnames: NA
    appversion: NA
    datadate: NA
---

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
library(knitr)
library(rmarkdown)
library(ggplot2)

# set knit options
opts_knit$set(progress=TRUE,verbose=TRUE)
opts_chunk$set(dev="CairoPNG",results="hold",fig.show="hold",fig.align="left",echo=FALSE,warning=FALSE,message=FALSE)
#options(knitr.table.format = "html") 
```

<img src="logo_scilifelab.svg" alt="logo" class="slogo">
<h1 class="toc-ignore rtitle">Zage Report</h1>
<h4 class="toc-ignore">`r format(Sys.Date(),format="%d-%b-%Y")`</h4>

---

|||  
|--|--|  
|Organism: |`r paste0("<b>",params$label,"</b>")`|  
|Genome type: |`r paste0("<b>",params$ome,"</b>")`|  
|Genome size (Gbp): |`r paste0("<b>",params$size,"</b>")`|  
|Total number of samples: |`r paste0("<b>",params$num_samples,"</b>")`|  
|Number of pools: |`r paste0("<b>",params$num_pools,"</b>")`|  
|Samples per pool: |`r paste0("<b>",params$samples_per_pool,"</b>")`|  
|Selected protocol: |`r paste0("<b>",params$protocol,"</b>")`|

---

```{r}
    as.datatable(params$table_long,
                 selection="none",
                 class="stripe hover",
                 style="bootstrap",
                 options=list(
                   dom="t",
                   paging=FALSE,
                   searchHighlight=TRUE,
                   autoWidth=FALSE,
                   columnDefs=list(list(className="dt-center",targets="_all"))),
                 callback = JS(paste0("var tipslong=['','",paste(params$table_long_colnames$Description,collapse="','"),"'],
                                       header=table.columns().header();
                                       for (var i=0; i<tipslong.length; i++) {
                                       $(header[i]).attr('title', tipslong[i]);
                                       }")))
```

__Table 1:__ Table showing lanes required, coverage and cost based on number of samples pooled per lane. Hover over header for descriptions.

```{r,fig.height=7,fig.width=7,dev="svg"}

dfr <- params$table_long_raw %>%
  select(samples_per_lane,reads_per_sample,lanes_req,coverage,cost_per_sample,cost_total) %>%
  gather(key=metric,value=value,-samples_per_lane) %>%
  mutate(metric=plyr::mapvalues(metric,from=c("cost_per_sample","cost_total",
                                                "coverage","lanes_req","reads_per_sample"),
                                  to=c("Cost Per Sample (SEK)","Cost Total (SEK)",
                                       "Coverage (X)","Lanes Required","Reads Per Sample (Millions)")))

ggplot(dfr,aes(x=as.factor(samples_per_lane),y=value,col=metric,group=metric))+
  #geom_bar(stat="identity")+
  geom_point()+
  geom_line()+
  scale_fill_manual(values=c("#7cb5ec","#434348","#90ed7d","#f7a35c","#8085e9",
                             "#f15c80","#e4d354","#2b908f","#f45b5b","#91e8e1"))+
  labs(x="Samples Per Lane",y="")+
  facet_wrap(~metric,nrow=5,scales="free_y")+
  #guides(colour=guide_colourbar(title="Reads Per Sample (Millions)"))+
  theme_bw(base_size=13)+
  theme(panel.border=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x=element_blank(),
        legend.position="none",
        legend.direction="horizontal",
        legend.justification="right",
        legend.title=element_text(vjust=0.5),
        strip.background=element_blank(),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_line(colour="grey60"))
```

__Figure 1:__ Barplot showing samples-per-lane vs various metrics.

---

`r paste0("<small>Zage version: ",params$appversion,". Data updated: ",params$datadate,". Report printed on ",Sys.Date(),".</small></br>")`


